Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities

### 2021-04-05 docs/manuscript/main.tex
#18 adds details on the guidelines for human experiments at UoB

\subsection*{Ethics}
All participants provided informed consent forms prior to participation in the experiment. Hence, the experiments were conducted in November 2016 and participants confirmed reading and understanding the participant information sheet of the experiments and were able to withdraw from the experiment at any time without giving any reason.
The design of the experiments adhered to the University of Birmingham regulations, data were anonymised and videos were stored only on a personal computer in accordance with the Data Protection Act 1998.
%Refer to Appendix D for further information about the ethics, online participation information sheets and experiment check list.

>>>>

\subsection*{Ethics}
All participants provided informed consent forms prior to participation in the experiment. Hence, the experiments were conducted in November 2016 and participants confirmed reading and understanding the participant information sheet of the experiments and were able to withdraw from the experiment at any time without giving any reason.
The design of the experiments adhered to the University of Birmingham guidelines and regulations for experiments with humans that includes: participant information sheet, checklist of the experiment and anonymised data collection in accordance with the Data Protection Act 1998.
All data in this study were anonymised and videos were stored only on a personal computer.
%Refer to Appendix D for further information about the ethics, online participation information sheets and experiment check list.
